This is a title

### 2021-05-15 manuscript/ms.tex
adds in initial departure point definitions

\subsection{Penetration depth measurements}

>>>>

\subsection{Penetration depth measurements}
In our evolved simulations, we find that the penetrative region has a nearly adiabatic stratification $\grad \approx \gradad$.
In order to characterize the vertical extent of the penetrative (and subsequent overshoot) region, we measure how drastically $\grad$ has departed from $\gradad$.
We define the difference between the adiabatic and radiative gradient,
\begin{equation}
\Delta\grad \equiv \gradad(z) - \gradrad(z).
\end{equation}
We measure penetration and overshoot depths in terms of ``departure points,'' that is, points at which the realized temperature gradient $\grad$ has evolved away from the adiabatic $\gradad$ by some fraction $f < 1$.
Specifically,
\begin{equation}
1 + \delta_{f} = \rm{max}(z) \mid \grad > \gradad - f\Delta\grad.
\end{equation}
In this work, we measure the 10\% ($\delta_{0.1}$), 50\% ($\delta_{0.5}$), and 90\% ($\delta_{0.9}$) departure points, which are respectively at the top of the penetration zone, in the middle of the overshoot zone, and at the top of the overshoot zone.
We find that these measurements based on the (slowly-evolving) thermodynamic profile are more robust and straightforward than many previous dynamically-based prescriptions \citep[see e.g.,][for a nice discussion]{pratt_etal_2017}.
